---
title: "R Notebook"
output: html_notebook
---

Require user inputs:
- User can define keyword groupings
- Make 5 groupings

Visuals based on keyword groupings:
- Simplify the BLM app into a daily outlook of yesterday's trends (TreeMap)
Drop the d3 treemap
Allow user to switch keyword grouping
Allow a weekly/monthly/annual view

- Index of many social issue discussions in America and mark any spikes with hover information (time-series)
Show the category tables below
> create_category_tables(category_group_2)

- Each social issue keywords have a historical volume index (histogram)

Visuals based on certain trends:
- Make an animated wordcloud for specific trends
- Make a chatter chart for trends
- Connected

```{r}
library(tidyverse)
library(lubridate)
library(tidytext)
library(extrafont)
library(SnowballC)
```

```{r}
desired_date_range <- seq(Sys.Date(), as.Date("2020-06-14"), by = -1)
```

```{r}
trend_csvs <- paste0("new_trends_", desired_date_range, ".csv")
tweet_csvs <- paste0("trend_tweets_", desired_date_range, ".csv")
```

```{r, warning = FALSE, message = FALSE}
tweets_df <- map_dfr(tweet_csvs, read_csv) %>%
  mutate(as_of = time_collected + hours(7)) # i don't think this is working right
```

```{r, warning = FALSE, error = FALSE, message = FALSE}
trends_df <- map_dfr(trend_csvs, read_csv)
```

```{r}
unnested_words <- tweets_df %>%
    unnest_tokens(word, text, token = "tweets", drop = FALSE) %>%
    mutate(stem = wordStem(word))
```

# User can pick words to find recent trends related to it.
## add hover to see tf-idf words related to trend
## Add direct trend link
## Try this? https://newsmap-js.herokuapp.com/
## can i save an Rdata object with the unnested tokens?

```{r}
#keyword trend monitor
term_trend_history <- function(words_of_interest) {
  p <- unnested_words %>%
    filter(time_collected >= "2020-05-23") %>%
    filter(word %in% words_of_interest) %>%
    mutate(date_label = paste(month(time_collected, label = TRUE), day(time_collected), year(time_collected))) %>%
    count(trend, date_label) %>%
    filter(tolower(trend) != tolower(words_of_interest)) %>%
    arrange(desc(n)) %>%
    mutate(date_collected = mdy(date_label)) %>%  
    group_by(date_collected) %>%
    mutate(rank = 1:n()) %>%
    ungroup() %>%
    filter(rank <= 25) %>%
    ggplot(aes(x = date_collected, y = rank)) +
    geom_label(aes(label = str_wrap(trend, 10), fill = n), 
               size = 2, 
               family = "IBM Plex Sans SemiBold") +
    scale_y_reverse() +
    scale_fill_gradient(low = "white", high = "#DDD92A") +
    scale_x_date(breaks = scales::date_breaks(width = "1 days"), 
                 labels = scales::label_date(format = "%m/%d"), position = "top") +
    labs(title = str_to_title(str_glue('Trends associated with "{words_of_interest}"')),
         y = "Strength of term",
         x = "") +
    coord_cartesian(clip = "off") +
    theme_minimal() +
      theme(text = element_text(family = "IBM Plex Sans SemiBold"),
        plot.title = element_text(family = "IBM Plex Sans SemiBold", size = 12, hjust = 0),
        plot.subtitle =  element_text(family = "IBM Plex Sans", size = 8),
        plot.caption = element_text(family = "IBM Plex Sans", size = 8, hjust = 0, colour = "grey50"),
        axis.text.y = element_blank(),
        axis.text.x = element_text(family = "IBM Plex Sans", size = 8),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        plot.margin = unit(c(1, 5, 1, 1), units = "cm"),
        legend.position = "none")
  
  return(p) 
}
```

# this is probably not as good as the treemap
## views by 3 days, this week, two weeks
## switch to ranking so all can be seen?

```{r, fig.height = 10, fig.width = 15}
term_trend_history("recession")
term_trend_history("climate")
term_trend_history("obama")
term_trend_history("racist")
term_trend_history("police")
term_trend_history("#blacklivesmatter")

# add hover with keywords?
```

```{r, fig.height = 8, fig.width = 12}
#keyword activity monitor
term_volume_history <- function(words_of_interest) {
  temp_df <- unnested_words %>%
    filter(word %in% words_of_interest) 
  
  p1 <- temp_df %>%
    filter(time_collected >= "2020-05-23") %>%
    ggplot(aes(x = time_collected)) +
    geom_histogram(bins = n_distinct(temp_df$time_collected)) +
    geom_hline(yintercept = 0) +
    scale_x_datetime(breaks = scales::date_breaks(width = "1 days"), labels = scales::label_date(format = "%m/%d")) +
    theme(axis.text.x = element_text(vjust = 2, angle = 90)) +
    labs(title = str_to_title(str_glue('Hourly Keyword Detection Across The Top 50 Active US Trends: "{str_to_title(words_of_interest)}"')),
         subtitle = "US Trends are collected through Twitter API. Fifty tweets are sampled from each active. The longer the trend lasts, the more tweets are sampled. If the keyword is trending, the spikes reflect this.")
  
  return(p1) 
}

term_volume_history("police")
```

```{r, message = FALSE, warning = FALSE, error = FALSE}
power_words <- c("#BlackLivesMatter", "Police", "Racist")

#tweets that have a power word stem in them
tweets_with_stem <- unnested_words %>%
  mutate(date_label = paste(month(time_collected, label = TRUE), day(time_collected), year(time_collected))) %>% # add this to data
  mutate(stem = wordStem(word)) %>%
  filter(stem %in% wordStem(tolower(power_words))) 

#list of trends with more than a couple power words
trends_wanted <- tweets_with_stem %>%
  count(trend, stem) %>%
  group_by(trend, stem) %>%
  summarize(total = sum(n)) %>%
  group_by(trend) %>%
  summarize(total = sum(total)) %>%
  distinct(trend) %>%
  .$trend

#trend popularity ranking
trend_popularity <- tweets_with_stem %>%
  filter(trend %in% trends_wanted) %>%
  count(trend, stem) %>%
  arrange(desc(n))

#all tweets of trends with a couple power words
all_tweets <- tweets_with_stem %>%
  filter(trend %in% trends_wanted) %>%
  mutate(date_label = paste(month(time_collected, label = TRUE), day(time_collected), year(time_collected)))

top_tweets <- all_tweets %>%
  group_by(trend) %>%
  filter(favorite_count == max(favorite_count)) %>%
  mutate(text = str_glue("{text}<br><a href={status_url}>View Tweet</a>")) %>%
  select(trend, text)

wordss <- all_tweets %>%
  filter(trend %in% trends_wanted) %>%
  unnest_tokens(word, text, token = "tweets") %>%
  anti_join(stop_words, by = "word") %>%
  count(word, trend) %>%
  filter(word != tolower(trend),
         word != str_remove(tolower(trend), "#"),
         word != "amp",
         !word %in% unwanted_words) 

keywords <- wordss %>%
  group_by(trend) %>%
  bind_tf_idf(word, trend, n) %>%
  arrange(desc(trend), desc(n)) %>%
  slice(1:10) %>%
  summarize(keywords = paste(word, collapse=", "))
```


```{r, fig.height= 30, warning = FALSE, error = FALSE, message = FALSE}
df <- unnested_words %>%
  filter(stem == "racist") %>%
  count(trend) %>%
  left_join(top_tweets) %>%
  left_join(keywords) %>%
  group_by(trend, text) %>%
  arrange(trend, desc(n)) %>%
  filter(row_number() == 1) %>%
  group_by(trend) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  mutate(rank = n():1) %>%
  #mutate(onclick = str_glue("window.open(\"{status_url}\")")) %>%
  mutate(text = str_replace_all(text, "'", "’")) %>%
  mutate(onclick = paste0( "alert(\"", text, "\")"))
  
p <- df %>%
  ggplot(aes(x = 0, y = rank)) +
  geom_text_interactive(aes(label = trend, size = n, 
                            tooltip = str_wrap(text, 35),  onclick = onclick, 
                            data_id = keywords),
                        show.legend = FALSE, family = "IBM Plex Sans") +
  scale_size(range = c(6, 8)) +
  scale_y_continuous(limits = c(1,max(df$rank)), 
                     expand = c(0, 1)) +
  theme_void() +
  labs(y = "Trend Popularity") +
  coord_cartesian(clip = "off")

pg <- girafe(ggobj = p, width_svg = 5, height_svg = 250) 

pg <- girafe_options(pg,
                     opts_hover(css = girafe_css(css= "fill:none;",
                                                 text = "stroke:none;fill:blue;")),
                     opts_sizing(rescale = TRUE, width = 0.8),
                     opts_tooltip(opacity = .8,
                                  offx = 20, offy = -10,
                                  use_fill = TRUE, use_stroke = TRUE,
                                  delay_mouseout = 1000))

htmlwidgets::saveWidget(pg, 
                        title = 'Twitter Trends Mentioning "Racist"',
                        file="race_pop.html", selfcontained = TRUE)

page_title <- tags$html(tags$head(tags$title('Racist & Anti-Racist Hall of Fame')))

title <- h2("Racist & Anti-Racist", 
             style = "font-family:Permanent Marker; color:#FFFFFFF")

title2 <- h1("Hall of Fame", 
             style = "font-family:Permanent Marker; color:#FFFFFFF")

body1 <- p("This page was created to highlight US Twitter trends with conversations mentioning the term", strong("Racist."), 
           style = "font-size:15px; font-family:Raleway; color:#FFFFFFF")

body2 <- p("Trends were sampled every hour. They are ranked based on",strong("keyword detection"),"and", strong("hours trending."), 
           style = "font-size:15px; font-family:Raleway; color:#FFFFFFF")

body3 <- p(strong("Hover"), "over a trend and see a popular tweet associated with it or...",
           style = "font-size:15px; font-family:Raleway; color:#FFFFFFF")

body4 <- p( strong("Click"), "on a trend to view the tweet (for mobile).",
           style = "font-size:15px; font-family:Raleway; color:#FFFFFFF")

body5 <- p("Congratulations to all who participated (=",
           style = "font-size:15px; font-family:Raleway; color:#FFFFFFF")
 
img <- a(img(src = here::here("Black_Lives_Matter.png"), 
             height = 100, width = 100, align = "right"), 
         href="https://secure.actblue.com/donate/ms_blm_homepage_2019")

#library(htmltools)

# Percent of total current trends containing "racist"

browsable(tagList(page_title, img, title, title2, tags$hr(), body1, body2, body3, body4, body5, pg))

beepr::beep(sound = "coin")
```

```{r}
save_html(tagList(page_title, img, title, title2, tags$hr(), body1, body2, body3, body4, body5, pg), file = "hof_racism.html")
```    

# Make a weekly view
# Make a daily snapshot

```{r, fig.height=12, fig.width=12}
library(treemap)
library(d3treeR)

treemap_trends <- function(words_of_interest, date_of_interest) {
  df <- unnested_words %>%
    filter(word %in% words_of_interest) %>%
    mutate(date_label = paste(month(as_of, label = TRUE), day(as_of), year(as_of))) %>% # add this to data
    count(trend, date_label) %>%
    filter(n > 1) %>%
    filter(tolower(trend) != tolower(words_of_interest)) %>%
    mutate(trend = str_wrap(trend, 10))

 d3tree3(treemap(df,
                index = c("date_label", "trend"),
                vSize = "n",
                vColor = "n",
                type = "manual",
                palette = "Blues", 
                range=c(0, 3000),
                algorithm = "pivotSize",
                fontsize.labels = 20,
                lowerbound.cex.labels = .2),
         rootname = str_to_title(str_glue('Twitter Trends associated with "Police"')), 
                width = "200%"
                )
}

tree <- treemap_trends("police", "2020-05-07")

tree
```

```{r}
unwanted_words <- c("people", "ill", "aint", "#covid19", "https", "didnt", "youre", "trend", "trends", "amp", "les", "des", "dont", "arent", "hes", "shes", "heres", "theyre", "yall", "watch", "time", "shit")

trends_of_interest <- unnested_words %>%
  filter(word %in% "police") %>%
  distinct(trend)

trends_tokenized <- unnested_words %>%
  filter(trend %in% trends_of_interest$trend) %>%
  filter(#!str_detect(word, "^@"),
    str_detect(word, "[a-z0-9-]+"),
    nchar(word) > 1,
    word != normalized_trend,
    word != str_remove(normalized_trend, "#"),
    !word %in% unwanted_words,
    !str_detect(word, "https")) %>%
  anti_join(stop_words, by = "word") %>%
  mutate(stem = wordStem(word))

trend_word_counts <- trends_tokenized %>%
  count(word, trend) 

# insert top words
important_word_df <- trend_word_counts %>%
  group_by(trend) %>%
  arrange(desc(trend), desc(n)) %>%
  slice(1:10)

keywords <- important_word_df %>%
  summarize(keywords = paste(word, collapse=", "))
```

```{r}
top_tweets <- tweets_df %>%
  filter(trend %in% trends_of_interest$trend) %>%
  group_by(trend) %>%
  filter(favorite_count == max(favorite_count)) %>%
  mutate(text = str_glue("{text} \n\n {status_url}")) %>%
  select(trend, text)
```

```{r}
DT::datatable(unnested_words %>%
                filter(word %in% "police") %>%
                mutate(date_label = paste(month(as_of, label = TRUE), day(as_of), year(as_of))) %>% # add this to data
                count(trend, date_label) %>%
                left_join(keywords) %>%
                left_join(top_tweets) %>%
                arrange(desc(n)))
```

```{r}
library(htmlwidgets)

saveWidget(tree, file="index.html", selfcontained = TRUE)
```

# group racists, racist and racism stems to "racis"

```{r}
trend_counts <- tweets_with_stem %>%
  count(trend, date_label, stem)

trend_term_df <- trend_counts %>%
  group_by(trend, date_label, stem) %>%
  summarize(trend_indicators = sum(n)) %>%
  spread(stem, trend_indicators) %>%
  replace(is.na(.), 0)

top_trend_counts <- trend_term_df %>%
left_join(trend_counts %>%
    group_by(trend, date_label) %>%
  summarize(total_indicators = sum(n)))

datatable(top_trend_counts %>%
            arrange(desc(total_indicators)) %>%
            rename(Trend = trend, `#BlackLivesMatter` = `#blacklivesmatt`, Police = polic, Racist = racist, `Total Indicators` = total_indicators))
```

